---
title: "Iteration and List Columns"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

set.seed(1)
```


## Lists

#### 1. vectors are limited to a single data class 

```{r}
vec_numeric = 5:8                           # all numeric
vec_char = c("My", "name", "is", "Jeff")    # all character
vec_logical = c(TRUE, TRUE, TRUE, FALSE)    # all logical

```

#### 2. lists can store vectors of different classes, including tables
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))    # a table can be stored in a list
l

```

#### 3. Lists can be accessed using names or indices

##### call by name
```{r}
l$vec_numeric   # list$vector name

```

##### call be index (use [[]])
```{r}
l[[1]]         # list[[1]]  the first item in a list, use double [[]]

```

##### call the index and then the range
```{r}
l[[1]][1:3]      # the range follows the index in a double [[]]

```

#### 4. dataframes are special lists -- each item has the same length


## **FOR** loops

#### 1. create a list and verify it by `is.list(list)`, get T OR F
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)

```

#### 2. load the function `mean_and_sd`

##### the argument x is for vectors, not lists. Thus, we cannot
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```


#### 3. apply the function to **each item** in list `list_norms`
```{r}
mean_and_sd(list_norms[[1]])

mean_and_sd(list_norms[[2]][3:4])

mean_and_sd(list_norms[[3]][1:10])

mean_and_sd(list_norms[[4]])

```

#### 4. use FOR loop to apply the function in 1 time

##### first, create an output vector in the mode of a **list** to store the result
##### because the function is for vector, it cannot take list as the argument
```{r}
output = vector("list", length = 4)    # vector(mode="list")

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}


typeof(output)     # the output is also a list

output[[1]]        # get the item in output using index

```


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```
