---
title: "Iteration and List Columns"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

set.seed(1)
```


## Lists

#### 1. vectors are limited to a single data class 

```{r}
vec_numeric = 5:8                           # all numeric
vec_char = c("My", "name", "is", "Jeff")    # all character
vec_logical = c(TRUE, TRUE, TRUE, FALSE)    # all logical

```

#### 2. lists can store vectors of different classes, including tables
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))    # a table can be stored in a list
l

```

#### 3. Lists can be accessed using names or indices

##### call by name
```{r}
l$vec_numeric   # list$vector name

```

##### call be index (use [[]])
```{r}
l[[1]]         # list[[1]]  the first item in a list, use double [[]]

```

##### call the index and then the range
```{r}
l[[1]][1:3]      # the range follows the index in a double [[]]

```

#### 4. dataframes are special lists -- each item has the same length


## **FOR** loops

#### 1. create a list and verify it by `is.list(list)`, get T OR F
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)

```

#### 2. load the function `mean_and_sd`

##### the argument x is for vectors, not lists. Thus, we cannot
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```


#### 3. apply the function to **each item** in list `list_norms`
```{r}
mean_and_sd(list_norms[[1]])

mean_and_sd(list_norms[[2]][3:4])

mean_and_sd(list_norms[[3]][1:10])

mean_and_sd(list_norms[[4]])

```

#### 4. use FOR loop to apply the function in 1 time

##### first, create an output vector in the mode of a **list** to store the result
##### because the function is for vector, it cannot take list as the argument
```{r}
output = vector("list", length = 4)    # vector(mode="list")

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}


typeof(output)     # the output is also a list

output[[1]]        # get the item in output using index

```


## Map

##### for loop is somtimes too complex

##### `map` function in `purrr` package can make it clearer

#### 1. `map(list, function)` the first argument is the list/vector/df to iterate over

##### `mean_and _sd()` 's output is a dataframe
```{r}
output = map(list_norms, mean_and_sd)

output

```

#### 2. use `.x`to specify the input list, and `~` to specify the function on that list
```{r}
output = map(.x = list_norms, ~ mean_and_sd(.x)) # use function as an argument in another function
output



```


```{r}
output = map(list_norms, median)
# output = map(.x = list_norms, ~ median(.x))

output

```

## Map Variants

#### 1. `map_dbl(list,function,.id="input"` when the output is double

##### the output of `median()` is double, so we can use `map_dbl`

##### becasue the output of median is not integer or logical, we cannot use `map_int` or `map_lgl

##### `id="input"` makes sure that we maintain the original list name in the output


```{r}
output = map_dbl(list_norms, median, .id = "input")

output

```

#### 2. `map_dfr()` is used when the output is data frame

##### this output result is more tidy than used in a FOR Loop

##### the FOR Loop will generate 4 separate df for the 4 items in a list

##### `map_dfr` can generate a single df to store the 4 items' result in 4 rows

```{r}
output = map_dfr(list_norms, mean_and_sd, .id = "input")

output

```


#### 3. `map_df()` is used in a pipeline

#### 4. map2() and map2_dbl(), map2_int(), map2_dfr() are for function with 2 arguments
```{r}
# output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))

```




## List Columns and Operations

#### 1. How we generate a list

##### list(item1 = vector1, item2 = vector2)

##### items are the names and the vectors are the content

##### the vectors can be from different classes
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

```


#### 2. create a df with a column of list

##### name is a character vector, samp is a list

##### tibble() can use vector and list to create a df

##### the column as a list is called the list column
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )

listcol_df

```

#### 2. `pull(column name)` from the df
```{r}
listcol_df %>% pull(name)   # pulled out a vector

listcol_df %>% pull(samp)   # pulled out a list

```

#### 3. the list column has all the properties as a list

##### the items in a list column can be called by index
```{r}
listcol_df$samp[[1]]


```

#### 4. map() can be applied to list columns as list
```{r}
map(listcol_df$samp, mean_and_sd)

```


#### 5. because the map() returns a list, it can be stored as a list column again.

##### this is often achieved by mutate(new_list = map(list_col,function))
```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd))  # create a summary list to store the list

listcol_df


```


## Nested Data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df

```

#### 1. `nest(df,list_name = col_i : col_j)` create a nested df

##### the list is created by combining the original columns
##### the list is a new column in the nested dataframe.
##### the list items(tibbles) are belong to the 3 names respectively

```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest

```


```{r}
weather_nest %>% pull(name)

```

#### 2. `pull(new list)` get 3 tibbles corresponding to the 3 names
```{r}
weather_nest %>% pull(data)
```

#### 3. the reverse operation is to `unnest(nest_df, cols = list)`
##### in this way we may restore the original data frame.
```{r}
unnest(weather_nest, cols = data)

```

#### 4. define a function using df as the argument
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

```


```{r}
weather_lm(weather_nest$data[[1]])

```

#### 5. `map(list,function)` list here is the listcol in a df
```{r}
map(weather_nest$data, weather_lm)

map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```


#### 6. `mutate(new_list = map(list,function))` create a new listcol taking value from map
```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest$models

```



