---
title: "Simulation"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

set.seed(1)

```


## Simulation: Mean and SD for one n

#### 1. write a function for simulation and estimates

##### summarize the simulated data
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {  # arguments with default
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),   # draw sample from normal distribution
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

```



#### 2. sampling distribution of population mean estimate 

##### because the `sim_mean_sd()` get data from normal distribution, we know mu hat follows normal distribution.
$$
\hat{\mu} \sim\left[\mu, \frac{\sigma}{\sqrt{n}}\right]
$$


#### 3. FOR loop to simulate 100 samples 

##### use for loop to draw 100 samples
##### `vector(mode="list")` create a list to store the output
##### `list[[i]]` use double [] to call the index refered item
##### `bind_rows(list)` combine the items by row
```{r}
output = vector("list", 100)     # vector(mode = "list") the output is a list

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)  # the items in the list are the results
}

sim_results = bind_rows(output)  # bind_rows(list) bind the list results by row

sim_results
```



#### 4. `map()` to simulate 100 samples
##### `expand_grid(x=,y=)` expand_grid creates a tibble
##### `map(sample_size, sim_mean_sd)` is a example of using `map()`
##### `map(argument,function)` is the correct usage the first item is the argument of the function
##### 
```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd) # sample_size is the argument of sim_mean_sd
  ) %>% 
  unnest(estimate_df)   # expand the list and get the results as 2 columns

sim_results_df


```


#### 5. examples of `expand_grid()`
##### can expand vector, df, matrix
##### can be used to quickly set up a tibble 
```{r}
expand_grid(x = 1:3, y = 1:2)

expand_grid(l1 = letters, l2 = LETTERS)  # letters and LETTERS are  character vector

expand_grid(df = data.frame(x = 1:2, y = c(2, 1)), z = 1:3)

expand_grid(x1 = matrix(1:4, nrow = 2), x2 = matrix(5:8, nrow = 2))

expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) 


```


#### 6. plot the simulation results
##### plot only with x specified
##### `geom_density()` generates the density plot (contour)
```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) +  
  geom_density()

```


####

```{r}
sim_results_df %>% 
  pivot_longer(                 # organize the mu_hat and sigma_hat from different samples
    mu_hat:sigma_hat,
    names_to = "parameter",     # use column name as category
    values_to = "estimate") %>% 
  group_by(parameter) %>%       # group by estimate category
  summarize(
    emp_mean = mean(estimate),  # calculate the mean of sample means
    emp_sd = sd(estimate)) %>%  # calculate the sd of sample sd's
  knitr::kable(digits = 3)      # make the output result in a well-formatted table


```


## Simulation: Mean for several n

#### 1. simulate samples with size of 20,60,120,240, each simulate 1000 times
```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)

sim_results_df
```


#### 2. plot the mu hat of samples of difference sample sizes

##### `str_c("string:",content)` connects the string and the content
##### `str_c` changes the original character string
##### `fct_inorder(column)` factorize and reorder the factors
##### x = factor , y = numeric, fill = factor
```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()


```

These estimates are centered around the truth (2) for each sample size, and the width of the distribution shrinks as sample size grows.


#### 3. usage of `str_c()`

```{r}
str_c("Letter: ", letters)

str_c("Letter", letters, sep = ": ")

str_c(letters, " is for", "...")

str_c(letters[-26], " comes before ", letters[-1])

str_c(letters, collapse = "")

str_c(letters, collapse = ", ")

# Missing inputs give missing outputs
str_c(c("a", NA, "b"), "-d")

# Use str_replace_NA to display literal NAs:
str_c(str_replace_na(c("a", NA, "b")), "-d")

````


#### 4. empirical mean and variance of these estimates 

##### mean and sd of sample means and sample variances

```{r}
sim_results_df %>% 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, sample_size) %>%  # group by 2 items
  summarize(
    emp_mean = mean(estimate),
    emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)

```



## Using rerun


#### 1. `purrr::rerun(times,function())` to iterate the function for many times, without changing the arguments(inputs).

```{r}
sim_results_df =   
  rerun(100, sim_mean_sd(30, 2, 3)) %>% 
  bind_rows()

sim_results_df
```



#### 2. FOR Loop + rerun()

##### the argument changes in the function and we still want to iterate for many times
##### create a list to contain the changed argument for the function
##### create a empty output list to store the results

```{r}
n_list = 
  list(
    "n_30"  = 30,   # item name in a list is character with ""
    "n_60"  = 60, 
    "n_120" = 120, 
    "n_240" = 240)

output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = rerun(100, sim_mean_sd(n_list[[i]])) %>% 
    bind_rows
}

output


```


#### 3. map() + rerun()

```{r}
sim_results_df = 
  tibble(sample_size = c(30, 60, 120, 240)) %>%  # create a tibble to put the arguments
  mutate(
    output_lists = map(.x = sample_size, ~rerun(1000, sim_mean_sd(n = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>%  # bind_rows(list)
  select(-output_lists) %>% 
  unnest(estimate_dfs)

sim_results_df
```


## Varying two simulation parameters

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60,120, 240),
    true_sd = c(6, 3),    # add an argument in the sim_mean_sd function
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df =  # map2() for 2 arguments in the function
      map2(.x = sample_size, .y = true_sd, ~sim_mean_sd(n = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)

```


```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() + 
  facet_grid(. ~ true_sd)

```