---
title: "Simulation"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

set.seed(1)

```


## Simulation: Mean and SD for one n

#### 1. write a function for simulation and estimates

##### summarize the simulated data
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {  # arguments with default
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),   # draw sample from normal distribution
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

```



#### 2. sampling distribution of population mean estimate 

##### because the `sim_mean_sd()` get data from normal distribution, we know mu hat follows normal distribution.
$$
\hat{\mu} \sim\left[\mu, \frac{\sigma}{\sqrt{n}}\right]
$$


#### 3. FOR loop to simulate 100 samples 

##### use for loop to draw 100 samples
##### `vector(mode="list")` create a list to store the output
##### `list[[i]]` use double [] to call the index refered item
##### `bind_rows(list)` combine the items by row
```{r}
output = vector("list", 100)     # vector(mode = "list") the output is a list

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)  # the items in the list are the results
}

sim_results = bind_rows(output)  # bind_rows(list) bind the list results by row

```



#### 4. `map()` to simulate 100 samples
##### `expand_grid(x=,y=)` expand_grid creates a tibble
```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)

sim_results_df

```

#### 5. examples of `expand_grid()`
##### can expand vector, df, matrix
##### can be used to quickly set up a tibble 
```{r}
expand_grid(x = 1:3, y = 1:2)
expand_grid(l1 = letters, l2 = LETTERS)  # letters and LETTERS are  character vector
expand_grid(df = data.frame(x = 1:2, y = c(2, 1)), z = 1:3)
expand_grid(x1 = matrix(1:4, nrow = 2), x2 = matrix(5:8, nrow = 2))
```





