---
title: "Writing Functions"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)

```

## Basic Function

####  1. calculate z score
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)  # sampled from a normal distribution

(x_vec - mean(x_vec)) / sd(x_vec)    # calculate the z score for the sample 

```


#### 2. writing a `z_score function(vector)` function to calculate z score
```{r}
z_scores = function(x) {      # function(argument) 
  
  z = (x - mean(x)) / sd(x)   # operation
  z                           # output
  
}

z_scores(x_vec)

```
#### 3. sample from the vector for sample size times

`sample(vector,sample size,replace)` 

```{r}
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))

```


#### 4. identify the data type and data length before operation

`is.numeric(vector)` judge if the vector is numeric, output is True or False

`length(x)==1` if the argument is a single value 

`stop("warning message")` when the data type is not satisfied, show the message

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {  
    stop("Argument x should be numeric")
  } 
  else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = x - mean(x) / sd(x)    # if -- else if -- else, else can be omitted
  
  z
}

```


## Multiple Outputs

#### 1. use list to show output

`list(output name 1 = output1, output name 2 = output 2)`

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x,    # output the multiple outputs in a list
       sd = sd_x)
}

mean_and_sd(x_vec)
```


#### 2. use df (tibble) to show the output

`tibble(output name 1 = output 1, output name 2 = output 2)`

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x,      # the out put is a tibble (data frame)
    sd = sd_x
  )
}
```



```{r}

```



```{r}

```