---
title: "Writing Functions"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)

```

## Basic Function

####  1. calculate z score
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)  # sampled from a normal distribution

(x_vec - mean(x_vec)) / sd(x_vec)    # calculate the z score for the sample 

```


#### 2. writing a `z_score function(vector)` function to calculate z score
```{r}
z_scores = function(x) {      # function(argument) 
  
  z = (x - mean(x)) / sd(x)   # operation
  z                           # output
  
}

z_scores(x_vec)

```
#### 3. sample from the vector for sample size times

`sample(vector,sample size,replace)` 

```{r}
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))

```


#### 4. identify the data type and data length before operation

`is.numeric(vector)` judge if the vector is numeric, output is True or False

`length(x)==1` if the argument is a single value 

`stop("warning message")` when the data type is not satisfied, show the message

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {  
    stop("Argument x should be numeric")
  } 
  else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = x - mean(x) / sd(x)    # if -- else if -- else, else can be omitted
  
  z
}

```


## Multiple Outputs

#### 1. use list to show output

`list(output name 1 = output1, output name 2 = output 2)`

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x,    # output the multiple outputs in a list
       sd = sd_x)
}

mean_and_sd(x_vec)
```


#### 2. use df (tibble) to show the output

`tibble(output name 1 = output 1, output name 2 = output 2)`

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x,      # the out put is a tibble (data frame)
    sd = sd_x
  )
}
```


## Multiple inputs

#### 1. 3 arguments and with defaults

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),  # use the arguments here
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)     
    )                     # the result of this operation is the output
}

sim_mean_sd(25,10,2)

```


## Example : Scraping Amazon
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```


```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```

## Functions as arguments

#### when to use : the inner function is used for many different objects
```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {   # summ_func should be filled with a function
  summ_func(x)                          # summ_func is just the argument name
}

```


```{r}
my_summary(x_vec, sd)   # sd the the function as the argument
```


```{r}
my_summary(x_vec, var)
```


```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)

```






